Verifying Demonstrations

### 2020-02-26 paper/DB-Schnorr-UWB.tex
Adds a result about the maximum advantage of any TF adversary (UWB)

>>>>

However, since there are \(m\) challenges, \(\S\) can probabilistically extract 
\(m p_{\adv}\) responses.
Once \(m p_{\adv} \geq 2\), \(\S\) can compute the secret~\(\alpha\) from two 
correct responses and \(p_{\S} = 1\) for any successive authentication.
This contradicts that the key is not leaked.
Hence, \(\epsilon < \frac{1}{m}\) or the adversary taints the session or the 
secret leaks.
This proves the following theorem.

\begin{theorem}
  The maximum advantage over random guessing for any \ac{DBTF} adversary is 
  strictly less than \(\frac{1}{m}\) per round.
\end{theorem}
